CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-20 paper.Rmd
More edits.

Historically, SEA practitioners have
analyzed the ECCs of individual countries
using linked spreadsheets,
often starting with primary- and final-stage data 
from the [IEA][link-iea]'s
world energy balances 
([WEB][link-ieaweb]s)
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa]. 
Data were stored in varying and inconsistent formats.
An early SEA database [@De-Stercke:2014]
estimated energy efficiencies 
of end-use machines using the economic status of countries,
thereby precluding use for energy-economy studies.

>>>>

Historically, SEA practitioners have
analyzed the ECCs of individual countries
using linked spreadsheets,
often starting with primary- and final-stage data 
from the [International Energy Agency][link-iea]'s (IEA's)
[world energy balances][link-ieaweb] (WEBs)
[@Ayres:2003ec; @Serrenho:2014aa; @Brockway:2014aa; @Brockway:2015aa]. 
Data were stored in varying and inconsistent formats.
An early SEA database [@De-Stercke:2014]
estimated energy efficiencies 
of end-use machines using the economic status of countries,
thereby precluding use in energy-economy studies.
